\chapter{Publications and Dissemination Activities}
\label{chapt|publications}

\section{Publications as Main Author}

\subsection {International Peer-Reviewed Journals}

\begin{itemize}
    \item{Lemaignan, S. and Ros, R. and Sisbot, E. A. Alami, R. and Beetz M., \textbf{Grounding the Interaction: Anchoring Situated Discourse in Everyday Human-Robot Interaction}, \textit{International Journal of Social Robotics}, 2011.}
\end{itemize}

\subsection {Book Chapters}

\begin{itemize}
    \item{\textbf{in press} Lemaignan, S. and Alami, R. and Pandey, A. K. and Warnier, M. and Guitton, J. , \textbf{Towards Grounding Human-Robot Interaction} in \textit{Bridges between the Methodological and Practical Work of the Robotics and Cognitive Systems Communities - From Sensors to Concepts} Editors: Amirat, T. and Chibani, A. and Zarri, G. P.. Springer Publishing. 2012.}
\end{itemize}

\subsection {Conference Articles}

\begin{itemize}
    \item{Lemaignan, S. and Ros, R. and Alami, R. and Beetz, M., \textbf{What are you talking about? Grounding dialogue in a perspective-aware robotic architecture}, \textit{ROMAN}. 2011.}
    \item{Lemaignan, S. and Ros, R. and Mösenlechner, L. and Alami, R. and Beetz, M., \textbf{ORO, a knowledge management module for cognitive architectures in robotics}, \textit{IROS}. 2010.}
    \item{Ros, R. and Lemaignan, S. and Sisbot, E. A. and Alami, R. and Steinwender, J. and Hamann, K. and Warneken, F., \textbf{Which One? Grounding the Referent Based on Efficient Human-Robot Interaction}, \textit{ROMAN}. 2010. \textbf{Best paper award}.}
\end{itemize}

\section{Publications as Co-Author}

\subsection {International Peer-Reviewed Journals}

\begin{itemize}
    \item{\textbf{in press} Lallée, S. and Pattacini, U. and Lemaignan, S. and Lenz, A. and Melhuish, C. and Natale, L. and Skachek, S. and Hamann, K. and Steinwender, J. and Sisbot, E.A. and Metta, G. and Pipe, T. and Alami, W. and Warnier, M. and Guitton, J. and Warneken, F. and Dominey, P.F., \textbf{Towards a Platform-Independent Cooperative Human-Robot Interaction System: III. An Architecture for Learning and Executing Actions and Shared Plans}, \textit{IEEE Transactions on Autonomous Mental Development}, 2012.}
\end{itemize}

\subsection {Conference Articles}

\begin{itemize}
    \item{\textbf{submitted} Warnier, M. and Guitton, J. and Lemaignan, S. and Alami, R., \textbf{Let’s clean the table together}, \textit{IROS}, 2012.}
    \item{Alami, R. and Warnier, M. and Guitton, J. and Lemaignan, S. and Sisbot, E. A., \textbf{When the robot considers the human...}, \textit{ISRR}, 2011.}
    \item{Lallée, S. and Pattacini, U. and Boucher J.D. and Lemaignan, S. and Lenz, A. and Melhuish, C. and Natale, L. and Skachek, S. and Hamann, K. and Steinwender, J. and Sisbot, E.A. and Metta, G. and Alami, W. and Warnier, M. and Guitton, J. and Warneken, F. and Dominey, P.F., \textbf{Towards a Platform-Independent Cooperative Human-Robot Interaction System: II. Perception, Execution and Imitation of Goal Directed Actions}, \textit{IROS}, 2011.} 
    \item{Lallée, S. and Lemaignan, S. and Lenz, A. and Melhuish, C. and Natale, L. and Skachek, S. and van Der Zant, T. and Warneken, F. and Dominey, P.F., \textbf{Towards a Platform-Independent Cooperative Human-Robot Interaction System: I. Perception}, \textit{IROS}, 2010.}
\end{itemize}


\section{Workshops and Other Dissemination Activities}

\subsection {2012}

\begin{itemize}
    \item{Echeverria, G. and Karg, M. and Lemaignan, S. and Degroote, A., and Lacroix, S., \textbf{MORSE Tutorial}, \textit{EURON}.}
    \item{Lemaignan, S. and Gharbi, M. and Mainprice, J. and Herrb, M. and Alami, R., \textbf{Roboscopie: A Theatre Performance for a Human and a Robot}, \textit{HRI}.}
    \item{Lemaignan, S. and Echeverria G. and Karg, M. and Mainprice, M. and Kirsch, A. and Alami, R., \textbf{Human-Robot Interaction in the MORSE Simulator}, \textit{HRI}.}
\end{itemize}

\subsection {2011}

\begin{itemize}
    \item{Lemaignan, S. and Ros, R. and Alami, R., \textbf{Dialogue in situated environments: A symbolic approach to perspective-aware grounding, clarification and reasoning for robots}, \textit{Grounding Human-Robot Dialog for Spatial Tasks - RSS workshop}.}
    \item{Lemaignan, S. and Sisbot, E. A. and Alami, R., \textbf{Anchoring interaction through symbolic knowledge}, \textit{HRI Pioneers}.}
\end{itemize}

\subsection {2010}

\begin{itemize}
    \item{Lemaignan, S., \textbf{Ontologies et robotique : Quand le robot donne du sens à ce qu'il perçoit}, \textit{DocToMe Seminar}.}
    \item{Lemaignan, S., \textbf{Knowledge centric architecture for Human-Robot interaction}, \textit{TUM/LAAS Joint Winter Workshop}.}
    \item{Lemaignan, S., \textbf{Ontologies for HRI}, \textit{Cotesys ROS Fall School}.}
    \item{Lemaignan, S., \textbf{What can we do with ontologies for HRI?}, \textit{Dagstuhl Seminar on Human-Robot Interaction}.}
    \item{Ros, R. and Sisbot, E. A. and Lemaignan, S. and Pandey, A. K. and Alami, R., \textbf{Robot, tell me what you know about...?: Expressing robot's knowledge through interaction}, \textit{ICAIR}.}
    \item{Lemaignan, S., \textbf{OpenRobots Ontology: an overview}, \textit{EURON}.}
\end{itemize}
